humanCdGF_predict_cfu

### 2016-10-26 code/HumanCdGF_predict_cfu.Rmd
update prediction/partial plots for colonize level

ggplot(data = all_rf, aes(x=observed, y=predicted, color = data)) + geom_point() + 
  # geom_abline(slope = 1) + 
  xlim(c(4,9)) + ylim(c(4,9)) +
  labs(x= 'Observed Log10 CFU', y = 'Predicted Log10 CFU',
       title = "Random Forest Prediction of Colonized C Difficile CFU from Day 0 Community") + 
  theme_bw() + annotate('text', x = 4.5, y = 8.5, # parse = T,
                        label=paste0('OOB ', 'R^2 == ', round(tail(rf_n_features$rsq, 1), 2),
                                     '\nLOcO ','R^2 == ', round(LOcO_rsq, 2),
                                     '\n1 mouse', 'R^2 == ', round(tail(om_rsq, 1), 2))) + 
  theme(legend.position = 'none')

get_tax(1, med_otu_importance$otu, tax_file)
##### - leave one cage out cv

ggplot(data = rf_prediction, aes(x=observed, y=predicted, color = cage_id)) + geom_point() + 
  labs(x= 'Observed CFU (log10)', y = 'Predicted CFU (log10)',
       title = "Random Forest Prediction of Colonized C Difficile CFU from Day 0 Community") + 
  theme_bw() + annotate('text', x=1.05*(min(rf_prediction$observed)), 
                        y=0.95*(max(rf_prediction$predicted)), parse = T,
                        label=paste0('R^2 == ', round(tail(rf_n_features$rsq, 1), 2))) + 
  theme(legend.position = 'none')

importance.df <- data.frame(get_tax(1, names(importance_final), tax_file),
                            importance = importance_final)
tax_label <- paste0(importance.df$tax_label, ' : ', 
                    round(importance.df$importance, 3))

cage_color <- rainbow(length(unique(rf_prediction$cage_id)))
for (i in seq_along(importance_final)) {
    partialPlot(rf_n_features, top_colonized_df, names(importance_final)[i],
                xlab='', main=paste(tax_label[i]))
    par(new = T)
    plot(y = top_colonized_df[ , 'log_cfu_med'],
         x = top_colonized_df[ , names(importance_final)[i]], 
         pch = 21, bg = 'gray', xlab = NA, ylab = NA, axes = F)
    axis(side = 4)
    mtext(side = 4, line = 3, 'Log10 CFU')
# To color points by cage - Change pch to 21 and un-comment following lines
#  for(m in seq_along(unique(rf_prediction$cage_id))){
#    cage <- unique(rf_prediction$cage_id)[m]
#    points(y = top_colonized_df[rf_prediction$cage_id %in% cage, 'log_cfu_med'],
#         x = top_colonized_df[rf_prediction$cage_id %in% cage , names(importance_final)[i]], 
#         pch = 21, bg = cage_color[m], xlab = NA, ylab = NA, axes = F)
#  }
}

```

>>>>

ggplot(data = all_rf, aes(x=observed, y=predicted, color = data)) + 
  geom_abline(color = 'gray', size = 0.5, linetype = 2, slope = 1) + 
  # geom_point() + 
  geom_smooth(method = 'lm', se = F) +
  stat_summary(fun.y=median, geom="point", aes(group = data)) + 
  stat_summary(fun.data = 'median_hilow') +
  xlim(c(5,9)) + ylim(c(5,9)) +
  labs(x= 'Observed Log10 CFU', y = 'Predicted Log10 CFU',
       title = "Random Forest Prediction of Colonized C Difficile CFU from Day 0 Community") + 
  theme_bw() + 
  scale_color_discrete(name = 'Model',
                       breaks = c('OOB', 'LOO', '1_mouse'),
                       labels = c(bquote('OOB (R'^'2'*' = '*.(round(tail(rf_n_features$rsq, 1), 2))*')'),
                                  bquote('LOO (R'^'2'*' = '*.(round(LOcO_rsq, 2))*')'),
                                  bquote('OM (R'^'2'*' = '*.(round(om_rsq,2))*')'))) + 
  theme(legend.justification=c(0,1), legend.position=c(0,1))

importance_om <- get_tax(1, med_otu_importance_om$otu, tax_file)

partial_df <- data.frame(colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    select(mouse_id, cage_id, log_cfu_med, one_of(rownames(importance_om))) %>% 
    filter(!is.na(log_cfu_med)))

color <- sapply(1:length(unique(partial_df$cage_id)), 
                           function(n)rgb(sample(c(0:255), 1),sample(c(0:255), 1),
                                          sample(c(0:255), 1), maxColorValue = 255))

layout(matrix(c(1:4), ncol=2, byrow=TRUE))
plot_loop_output <- lapply(seq_along(importance_om$tax), function(i){
    partialPlot(rf_n_features, top_colonized_df, rownames(importance_om)[i],
                xlab='', main=paste(importance_om$tax_label[i]))
    par(new = T)
    plot(y = top_colonized_df[ , 'log_cfu_med'],
         x = top_colonized_df[ , rownames(importance_om)[i]], 
         pch = 21, bg = 'gray', xlab = NA, ylab = NA, axes = F)
    axis(side = 4)
    mtext(side = 4, line = 3, 'Log10 CFU')
# To color points by mouse - Change pch to 21 and un-comment following lines
  lapply(seq_along(unique(partial_df$cage_id)), function(m){
    mouse <- unique(partial_df$cage_id)[m]
    points(y = partial_df[partial_df$cage_id %in% mouse, 'log_cfu_med'],
           x = partial_df[partial_df$cage_id %in% mouse , rownames(importance_om)[i]], 
           pch = 21, cex = 2, bg = color[m], xlab = NA, ylab = NA, axes = F)
  })
})
rm(plot_loop_output)
```
